---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/Bartesto/wk4pkg.svg?branch=master)](https://travis-ci.org/Bartesto/wk4pkg)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/Bartesto/wk4pkg?branch=master&svg=true)](https://ci.appveyor.com/project/Bartesto/wk4pkg)

###wk4pkg README
This package contains a collection of functions that will aid in the loading, analysing and visualisation of Fatality Analysis Reporting System [(FARS)](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) data.

###Requirements
This package must be installed from GitHub. You can use the following code to install it:
```{r, eval=FALSE}
library(devtools)
install_github("Bartesto/wk4pkg")
library(wk4pkg)
```

The package has dependencies with dplyr, tidyr, readr and maps. On installation you may be prompted to install additional packages.

###Help Files
All functions contained in wk4pkg have their own help files and there is also a package vignette with a suggested workflow.