---
title: "Using wk4pkg"
author: "Bart Huntley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using wk4pkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
The Fatality Analysis Reporting System (FARS) collates accident data and is available from the [National Highway Traffic Safety Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars). The functions contained in the wk4pkg are designed to help access and summarise this data.

What follows is a guide on how to use each of the functions.

###make_filename
Downloading data from FARS will result in annual compressed .csv files. The function **make_filename** constructs the correctly formatted .csv filename, enabling the resulting object to be passed directly to other wk4pkg functions. For example:
```{r, eval=TRUE, message=FALSE}
# Load the package and other helpful packages
library(wk4pkg)
library(dplyr)

# Make a file name for the year 2013 and store in an object called 'fname'
fname <- make_filename(2013)

print(fname)
```


###fars_read
Now that we have a filename it is easy to read in some data.
```{r, eval=TRUE, echo=FALSE}
fname <- system.file("extdata", fname, package = "wk4pkg")
```

```{r, eval=TRUE}
# Here we will read in the data and create an object called 'FARS2013'
FARS2013 <- fars_read(fname)

# Use dplyr's glimpse function to see the data
glimpse(FARS2013)
```

###fars_read_years
This function will take a vector of years and return a list containing tibbles of years and months in which fatal traffic accidents occured.
```{r, eval=TRUE}
# Make a vector of years for which you have downloaded data
years <- c(2013, 2014, 2015)

# Use the function to create a list called 'allyears'
allyears <- fars_read_years(years)

# Use dplyr's glimpse function to see the data
glimpse(allyears)

```


###fars_summarize_years
This function again takes a vector of years but returns a summary of the number of fatal accidents per month per year in a tibble.
```{r, eval=TRUE}
# Make a vector of years for which you have downloaded data
years <- c(2013, 2014, 2015)

# Use the function to create a tibble summarising fatalities per month
summary <- fars_summarize_years(years)

# Use dplyr's glimpse function to see the data
glimpse(summary)
```

###fars_map_state
The final function in this package creates a black and white state map showing the locations of fatal accidents by providing a State number and year.
```{r, eval=TRUE, warning=FALSE}
# This function uses functions from the 'maps' package
library(maps)

# To make the map provide a State number and year of interest (e.g. for fatalities in California in 2013)
fars_map_state(6, 2013)
```














